\documentclass[10pt,a4paper,times]{moderncv} 
\moderncvstyle{banking}

\usepackage[utf8]{inputenc} 
\usepackage[left=1cm, right=1cm, top=1cm, bottom=1cm]{geometry}
\usepackage{import}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{fontawesome}
\usepackage[hidelinks]{hyperref}
\usepackage{tfrupee}

% Redefinition, symbol included in link:
\let\orighref\href
\renewcommand{\hrefer}[2]{\orighref{#1}{#2\,\faExternalLink}}

\thispagestyle{empty} 

\begin{document}
\centerline{\Large{\textbf{Hemant Ghuge}}}

\begin{center}
    \faLinkedin\hspace{0.2cm}\href{https://www.linkedin.com/in/hemantghuge/}{linkedin.com/in/hemantghuge}
    \hspace{0.2cm}
    \faGithub\hspace{0.2cm}\href{https://github.com/hemantghuge}{github.com/hemantghuge}
    \hspace{0.2cm}
    \faGoogle\hspace{0.2cm}\href{mailto:hemantgghuge@gmail.com}{hemantgghuge@gmail.com}
    \line(1,0){520}
\end{center}

{\textbf{\large{EDUCATION:}}}\\

\begin{itemize}

    \item{\cventry{Aug 2016 -- Present}{Bachelor of Engineering in Electronics and Telecommunication, CGPA - 7.67 (Till 7th Semester) }{\hrefer{https://www.gcoeara.ac.in/}{Government College of Engineering and Research}}{Avasari(Khurd), Pune}{}{\vspace{3pt}}}

\vspace{0.2cm}

\end{itemize}

{\textbf{\large{INTERNSHIPS:}}}\\

\begin{itemize}

    \item{\cventry{Aug 2020 -- Present}{Computer Vision Intern}{\hrefer{https://www.tarsyer.com/}{Tarsyer}}{Koregaon Park, Pune}{}{\vspace{3pt}}}
    
    \vspace{-0.2cm}
    
    \begin{itemize}
        \item Achieved accuracy \textbf{99\%} by creating TFLite Model with collaboration - 10 error in 1000 objects
        \item Detection, Tracking, Counting, Deployment as per \textbf{customer requirement}.
        \item \textbf{Technologies Used:-} TensorFlow, TFLite, OpenCV, Deep Learning, Raspberry Pi, Flask\\
    \end{itemize}
    
\vspace{0.2cm}

\end{itemize}

{\textbf{\large{PROJECTS:}}}\\

\begin{itemize}
    
    \item{\cventry{Jul 2020 -- Aug 2020}{Summer Research Trainee}{Wall-Climbing Robot with Dual-Manipulator for Cleaning and Painting for a Concrete Surface}{\href{http://www.neist.res.in/srtp2020/index.php}{CSIR-CBRI}}{\textbf{\href{https://scholar.google.com/citations?user=NdEmHUAAAAAJ&hl=en}{Guide: Er. Ravindra Singh Bisht}}}{\vspace{3pt}}}
    
    \vspace{-0.2cm}
    
    \begin{itemize}
        \item Designed and developed control strategies for a wall-climbing robot having dual-arm.
        \item \textbf{Technologies Used:-} Proteus, SolidWorks, Arduino\\
    \end{itemize}

\vspace{0.2cm}

    \item{\cventry{Jul 2019 -- Jun 2020}{Team Representative, Computer Vision, Robotics}{\hrefer{https://www.youtube.com/watch?v=_118klFem0o&t=2s}{\textit{[UG PROJECT]} Smart and Efficient Techniques for Automated Guided Vehicle}}{Avasari(Khurd), Pune}{\textbf{\href{https://scholar.google.com/citations?user=NdEmHUAAAAAJ&hl=en}{Guide: Dr. Kirti Vasant Thakur}}}{\vspace{3pt}}}
    
    \vspace{-0.2cm}
    
    \begin{itemize}
        \item \textbf{3rd} in ABHIKALP 2020 \& \textbf{Top 4\%} (49 out of 1346 teams) in e-Yantra Ideas Competition 2020.
        \item Computer Vision, Control System, Path Planning for performing various \textbf{Industrial-Based Task}.
        \item \textbf{Technologies Used:-} Python, OpenCV, TensorFlow, Raspberry Pi, Arduino\\
    \end{itemize}

\vspace{0.2cm}

    \item{\cventry{Jul 2019 -- Oct 2019}{Team Captain}{\hrefer{https://in.mathworks.com/academia/student-competitions/minidrones.html}{MathWorks MiniDrone Competition, 2019}}{NUMA, Bangalore}{Image Processing, Control System}{\vspace{3pt}}}
    
    \vspace{-0.2cm}
    
    \begin{itemize}
        \item \textbf{Ranked 5th} in the final round. Amazing \textbf{mentorship} from the \textbf{Technical Evangelist} of MathWorks.
        \item Designed a line follower and \textbf{angle estimation algorithm} for a Mini-Drone. It includes Model-Based-Design.
        \item \textbf{Technologies Used:-} MATLAB, Simulink, Computer Vision and Control System Toolbox\\
    \end{itemize}

\vspace{0.2cm}

    \item{\cventry{Sep 2018 -- Apr 2019}{Team Representative}{ \hrefer{https://www.youtube.com/watch?v=8FT0MLcASMA}{Fire Rescue System (FRS) for High-Rise Building}}{IIT, Bombay}{Inventor, Robotics}{\vspace{3pt}}}
    
    \vspace{-0.2cm}
    
    \begin{itemize}
        \item Finished in \textbf{Top 2\%} (21 out of 1000+ teams) in e-Yantra Ideas Competition 2019.
        \item \textbf{\rupee 5000} as cash prize and special pass to e-Yantra National Symposium 2019.
        \item Developed a secondary evacuation system. Appended speed-varing feature for the operator/rescuer.\\
    \end{itemize}
    
\vspace{0.2cm}

    \item{\cventry{Team of 40 students}{Senior Team Member}{ \hrefer{https://en.wikipedia.org/wiki/Robocon_India}{National DD Robocon India}}{}{\href{https://rrlgcoeara.in/}{Robotics Research Lab}}{\vspace{3pt}}}
    
    \begin{center}
        \begin{tabular}{ p{70}  p{180}   p{80}   p{80}   p{90}  }
        \hline
        \textbf{Edition} & \textbf{Award} & \textbf{Rank} & \textbf{Venue} & \textbf{Timeline}\\ [0.3ex] \hline
        \hrefer{https://www.youtube.com/watch?v=-J3ZOYKO1EA}{18$^{th}$ } & Judges Special Award  & 4$^{th}$ & IIT, Delhi & Sep 2018 -- Jun 2019 \\ 
        \hrefer{https://www.youtube.com/watch?v=6Fx7XCBI0dA}{17$^{th}$ } & Smart and Simple Robot Award & 2$^{nd}$(League) &  Balewadi, Pune & Sep 2017 -- Mar 2018 \\
        \end{tabular}
    \end{center}
    
    \vspace{0.2cm}
    
    \begin{itemize}
        \item In every edition, we built \textbf{two 20kg}(apx.) \textbf{Manipulator} based \textbf{Mobile Robot} for performing multiple tasks. 
        \item Tasks such as navigation, obstacle avoidance, picking, throwing, transferring etc. were executed.\\ 
    \end{itemize}
    
\vspace{0.2cm}

\end{itemize}

{\textbf{\large{RESEARCH PUBLICATION:}}}\\

\vspace{-0.2cm}

\begin{itemize}

    \item \textbf{Hemant Ghuge}, Revati Kulkarni, et$.$ al.\hrefer{https://ieeexplore.ieee.org/document/9128377}{\textit{"Fire Rescue System for High Rise Building"}}, \textbf{5th IEEE International Conference On Computing, Communication, Control And Automation (ICCUBEA)}, 19-21 Sept. 2019. \textbf{Best Paper}(In Session)
    
    \vspace{0.2cm}
    
    \item Unnati Kulkarni, \textbf{Hemant Ghuge}, et$.$ al.\hrefer{https://www.springer.com/gp/book/9789811583902}{\textit{"An Algorithm for Skew Angle Estimation and it’s Application Domain"}}. In: Merchant et$.$ al., (eds) \textbf{Advances in Signal and Data Processing}. Select Proceedings of ICSDP 2019, 15-16 Nov. 2019, \textit{Lecture Notes in Electrical Engineering}, vol. 703. \textbf{Springer, Singapore}
    
    \vspace{0.2cm}
    
    \item Tejas Chaudhari, \textbf{Hemant Ghuge} et$.$ al.\hrefer{https://ieeexplore.ieee.org/document/9105783}{\textit{"Design and Control of Quadruped Robot along with Machine Vision based Path Planning"}}, \textbf{IEEE Pune Section International Conference (PuneCon)}, 18-20 Dec. 2019

\end{itemize}

\end{document}
